Output Summary

### 2021-07-23 03-post-process/output-plots.Rmd
Add new monitored output to the output plots

@@

# Smolt-to-Adult Rates

@@

@@

```{r}
# extract posterior summaries
alpha_summ = post_summ(post, "alpha", digits = 0)
beta_summ = post_summ(post, "beta", digits = -3)
sigma_summ = post_summ(post, "sigma_Pb", digits = 2)

# create/format the table
tab = cbind(alpha_summ, beta_summ, sigma_summ)
colnames(tab) = c("$\\alpha$", "$\\beta$", "$\\sigma_{Pb}$")

>>>>

## Time Stamps

```{r}
df = data.frame(Value = model_info$jags_time)
rownames(df) = c("Time Started", "Time Ended", "Time Elapsed")
kable(df) %>%
  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
  column_spec(1, bold = TRUE)
```

@@

# Equivilency Rates

## Smolt-to-Adult Rates

@@

## Parr per Spawner

"Spawner" means total spawners that survive pre-spawn mortality.

```{r}
par(oma = c(1,1,0,0))
plot_tseries(est = post_summ(post, "Pb_per_Sa_tot["), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]))
mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Parr/Spawner")
```

## Smolt per Spawner

"Smolt" means total NOR smolt that survive their second winter, immediately prior to migration out of basin.

```{r}
par(oma = c(1,1,0,0))
plot_tseries(est = post_summ(post, "Mb_per_Sa_tot["), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]))
mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Smolt/Spawner")
```

## Spawners per Spawner

This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adult recruits returning across multiple ages/years). "Brood year" refers to the year the returning production was spawned.

```{r}
all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])

par(oma = c(1,1,0,0))
plot_tseries(est = post_summ(post, "Sa_tot_per_Sa_tot["), yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)])
mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Spawners/Spawner")
abline(h = 1, lty = 2)
```

@@

```{r}
# extract posterior summaries
alpha_summ = post_summ(post, "alpha", digits = 0)
beta_summ = post_summ(post, "^beta$", digits = -3)
beta_per_peu_summ = post_summ(post, "beta_per_peu", digits = -1)
sigma_summ = post_summ(post, "sigma_Pb", digits = 2)

# create/format the table
tab = cbind(alpha_summ, beta_summ, beta_per_peu_summ, sigma_summ)
colnames(tab) = c("$\\alpha$", "$\\beta$", "$\\beta/\\mathrm{PEU}$", "$\\sigma_{Pb}$")
